Studying public transit API query logs\\ to get an indication of travel flows

### 2015-12-22 paper.tex
remove random

The \emph{iRail} project\footnote{\url{http://hello.irail.be}} started in 2008 to make the data of the Belgian railway accessible for developers.
Ever since, the project offers developer both a GTFS data dump for third party apps and a route planning API.
The query logs of this API has been stored since 2013.
Our hypothesis is that, while we should study the data with high level of sceptisicm (given enough data, you can find any pattern), our data will be better than random data.

>>>>

The \emph{iRail} project\footnote{\url{http://hello.irail.be}} started in 2008 to make the data of the Belgian railway accessible for developers.
Ever since, the project offers developer both a GTFS data dump for third party apps and a route planning API.
The query logs of this API has been stored since 2013.
Our hypothesis is that, while we should study the data with high level of sceptisicm (given enough data, you can find any pattern), \todo{\ldots}
